---
title: "Watershed Assessment Unit Analysis"
subtitle: "Layer Summary"
author: "Environmental Reporting BC"
date: "24/1/2022"
output: pdf_document
number_sections: true 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source('header.R')
source('packages.R')
```

```{r load gpkg, include=FALSE}
wau_analysis <- st_read("data/wshd_w_elements.gpkg", crs=3005) %>%
  st_cast(to="MULTIPOLYGON") %>%
  st_make_valid() %>%
  st_drop_geometry()

```


This document provides background information for processing the `r element` layer. 


```{r}
# Bring in data dictionary details here 
# - version number
# - data source (where is file saved)
# - important derivation methods

```

 
# Layer Analysis

Depending on the layer, different transformations will fit the data best, but due to data type, most will have skewed right distributions (long right tail). Here we have created a log transformation column (for right-skewed data) and a square root transformation column (for left skewed data) to test which transformation is the right fit. Note that 0's were removed and made 'none'. Below we have also included plots for a natural breaks (Jenks) transformation, which is best suited to  data that is unevenly distributed but not skewed towards either end of the distribution.

```{r f_own, echo=FALSE, results='asis'}
wau_working <- wau_analysis %>%
  mutate(og_perc = round(OG_ha/ASSESSMENT_UNIT_AREA_HA*100, 2)) %>%
  mutate(log_OG = ifelse(OG_ha>0, log(OG_ha), NA)) %>%
  mutate(sqrt_OG = ifelse(OG_ha>0, sqrt(OG_ha), NA)) # for right-skewed data

wau_jenks <- getJenksBreaks(wau_analysis$OG_ha, 6)

new_layer_summary <- wau_working %>%
  filter(OG_ha > 0) %>%
  summarise(r_mean = signif(mean(OG_ha, 3)),
            r_med = signif(median(OG_ha, na.rm = TRUE), 3),
            r_20 = signif(quantile(OG_ha, prob=0.20, na.rm = TRUE), 3),
            r_40 = signif(quantile(OG_ha, prob=0.40, na.rm = TRUE), 3),
            r_60 = signif(quantile(OG_ha, prob=0.60, na.rm = TRUE), 3),
            r_80 = signif(quantile(OG_ha, prob=0.80, na.rm = TRUE), 3),
            r_95 = signif(quantile(OG_ha, prob=0.95, na.rm = TRUE), 3),
            r_min = signif(min(OG_ha, na.rm = TRUE), 3), #indicates this value is half lowest MDL
            r_max = signif(max(OG_ha, na.rm = TRUE), 3),
            r_n = length(OG_ha))%>% 
  mutate(transformation = "raw")

new_layer_summary_log<- wau_working %>%
  summarise(r_mean = signif(mean(log_OG, 3)),
            r_med = signif(median(log_OG, na.rm = TRUE), 3),
            r_20 = signif(quantile(log_OG, prob=0.20, na.rm = TRUE), 3),
            r_40 = signif(quantile(log_OG, prob=0.40, na.rm = TRUE), 3),
            r_60 = signif(quantile(log_OG, prob=0.60, na.rm = TRUE), 3),
            r_80 = signif(quantile(log_OG, prob=0.80, na.rm = TRUE), 3),
            r_95 = signif(quantile(log_OG, prob=0.95, na.rm = TRUE), 3),
            r_min = signif(min(log_OG, na.rm = TRUE), 3), #indicates this value is half lowest MDL
            r_max = signif(max(log_OG, na.rm = TRUE), 3),
            r_n = length(log_OG)) %>% 
  mutate(transformation = "log")

new_layer_summary_sqrt<- wau_working %>%
  summarise(r_mean = signif(mean(sqrt_OG, 3)),
            r_med = signif(median(sqrt_OG, na.rm = TRUE), 3),
            r_20 = signif(quantile(sqrt_OG, prob=0.20, na.rm = TRUE), 3),
            r_40 = signif(quantile(sqrt_OG, prob=0.40, na.rm = TRUE), 3),
            r_60 = signif(quantile(sqrt_OG, prob=0.60, na.rm = TRUE), 3),
            r_80 = signif(quantile(sqrt_OG, prob=0.80, na.rm = TRUE), 3),
            r_95 = signif(quantile(sqrt_OG, prob=0.95, na.rm = TRUE), 3),
            r_min = signif(min(sqrt_OG, na.rm = TRUE), 3), #indicates this value is half lowest MDL
            r_max = signif(max(sqrt_OG, na.rm = TRUE), 3),
            r_n = length(sqrt_OG)) %>% 
  mutate(transformation = "sqrt")

summary <- bind_rows(new_layer_summary, new_layer_summary_log, new_layer_summary_sqrt)
```

# Figures

```{r f_own plots, echo=FALSE, warning=FALSE, results='asis'}
#hist - raw data
dist<-ggplot(data=wau_working) +
  geom_histogram(mapping = aes(x=OG_ha), binwidth = 50) +
  ggtitle("Raw Data (No Transformations Applied)")
dist

# hist - log data
dist_log<-ggplot(data=wau_working) +
  geom_histogram(mapping = aes(x=log_OG), binwidth = 0.1) +
  ggtitle("Log Transformed Data") 
dist_log 

#qq plot - normality test
log_qq <- ggqqplot(wau_working$log_OG) +
  ggtitle("Normality Test - Log Transformed Data")
log_qq

ks.test(wau_working$log_OG, "pnorm")

# hist - sqrt data
dist_sqrt<-ggplot(data=wau_working) +
  geom_histogram(mapping = aes(x=sqrt_OG), binwidth = 5) +
  ggtitle("Square Root Transformed Data") 
dist_sqrt

#qq plot - normality test
sqrt_qq <- ggqqplot(wau_working$sqrt_OG) +
  ggtitle("Normality Test - Square Root Transformed Data")
sqrt_qq


#normality-test - sqrt
ks.test(wau_working$sqrt_OG, "pnorm")

plot(wau_jenks, main = "Old Growth Data - Natural Breaks (Jenks) Transformation")

#Classify based on percentiles
wau_ranking <- wau_working %>%
  mutate(og_rank = case_when(
    OG_ha == 0 ~ 'None',
    OG_ha > 0 & OG_ha <= new_layer_summary$r_20 ~ 'Negligible',
    OG_ha > new_layer_summary$r_20 & OG_ha <= new_layer_summary$r_40 ~ 'Low',
    OG_ha > new_layer_summary$r_40 & OG_ha <= new_layer_summary$r_60 ~ 'Medium',
    OG_ha > new_layer_summary$r_60 & OG_ha <= new_layer_summary$r_80 ~ 'High',
    OG_ha > new_layer_summary$r_80 & OG_ha <= new_layer_summary$r_max ~ 'VeryHigh'
  ),
  og_rank_log = case_when(
    OG_ha == 0 ~ 'None',
    log_OG >= new_layer_summary_log$r_min & log_OG <= new_layer_summary_log$r_20 ~ 'Negligible',
    log_OG > new_layer_summary_log$r_20 & log_OG <= new_layer_summary_log$r_40 ~ 'Low',
    log_OG > new_layer_summary_log$r_40 & log_OG <= new_layer_summary_log$r_60 ~ 'Medium',
    log_OG > new_layer_summary_log$r_60 & log_OG <= new_layer_summary_log$r_80 ~ 'High',
    log_OG > new_layer_summary_log$r_80 & log_OG <= new_layer_summary_log$r_max ~ 'VeryHigh'), 
  og_rank_sqrt = case_when(
    OG_ha == 0 ~ 'None',
    sqrt_OG >= new_layer_summary_sqrt$r_min & log_OG <= new_layer_summary_sqrt$r_20 ~ 'Negligible',
    sqrt_OG > new_layer_summary_sqrt$r_20 & log_OG <= new_layer_summary_sqrt$r_40 ~ 'Low',
    sqrt_OG > new_layer_summary_sqrt$r_40 & log_OG <= new_layer_summary_sqrt$r_60 ~ 'Medium',
    sqrt_OG > new_layer_summary_sqrt$r_60 & log_OG <= new_layer_summary_sqrt$r_80 ~ 'High',
    sqrt_OG > new_layer_summary_sqrt$r_80 & log_OG <= new_layer_summary_sqrt$r_max ~ 'VeryHigh')
  )

#stargazer(wau_ranking[23:50], title = "Summary - Data Classed by Percentiles")




ggplot(data=wau_ranking, mapping=aes(x=aqua_id, y=OG_ha, color = og_rank))+
  geom_boxplot() 

```
