---
output:
  md_document:
    variant: markdown_github
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


[![img](https://img.shields.io/badge/Lifecycle-Experimental-339999)](https://github.com/bcgov/repomountie/blob/master/doc/lifecycle-badges.md)


# na-wau-layers

## Usage

The na-wau-layers repository processes new B.C. geospatial layers and adds them into the WAU Biodiversity Layer. The process uses the most recent version of the WAU Biodiversity Layer, adds the new information, and re-writes a new version of the WAU Biodiversity Layer. 

To process new layers, there are several important steps and considerations. 

### Considerations

- The WAU Biodiversity Layer currently considers areas outside of current Parks and Protected Areas and Other Area-Based Conservation Measures (OECMs) current to 2021. New layers do not necessarily need to follow this standard, but users should be aware of the current data extent. 
- Layers should be clean and ready to use prior to inclusion in the WAU Biodiversity Layer.
- There are processing options throughout for vector or raster files. It is up to the user to decide what type of file to use. 
- For **area-only metrics** - _**raster**_ processing will be faster. The `01_load.R` script ensures the raster is in Hectares BC format prior to processing. 
- For **additional metrics** are required (e.g. species number, species name) - processing should likely be done in _**vector**_ format. 

### Processing Steps

The first step in processing a new layer is to fill in the `header.R` file. An example is below using old-growth data.

#### Header Example

```{r header-example}
#update with file of interest
spatialOutDir <- "out/"
layer_file <- file.path("data/old-growth/old-growth.shp")
out_dir <- file.path("out/old-growth/")
dir.create(out_dir) #creates an output folder
element <- 'priority_old_growth'  # use underscores only, used as a file name but also column name
```

After the header script is completed, there are 4 (or 5 for vector) scripts that need to be run in order:

- `01_load.R`
- `02_intersect_wau.R`
- `03_binning.R`
- `04_vector-metrics.R` - only use with vector inputs
- `05_output.R` 

There is an optional .rmd script (`04_analysis_sample.Rmd`) that will produce a metadata file for the layer after is it processed.  

### Getting Help or Reporting an Issue

To report bugs/issues/feature requests, please file an [issue](https://github.com/bcgov/na-wau-layers/issues/).

### How to Contribute

If you would like to contribute, please see our [CONTRIBUTING](CONTRIBUTING.md) guidelines.

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.

### License

```
Copyright 2021 Province of British Columbia

Licensed under the Apache License, Version 2.0 (the &quot;License&quot;);
you may not use this file except in compliance with the License.
You may obtain a copy of the License at

http://www.apache.org/licenses/LICENSE-2.0

Unless required by applicable law or agreed to in writing, software distributed under the License is distributed on an &quot;AS IS&quot; BASIS,
WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
See the License for the specific language governing permissions and limitations under the License.
```

---
*This project was created using the [bcgovr](https://github.com/bcgov/bcgovr) package.* 
